\documentclass[12pt, russian, a4paper]{article}

\input{inc/pre}

\begin{document}
    \input{inc/titlepage}
    \setcounter{page}{2}

    \tableofcontents
    
    \newpage
    \input{inc/0-introduction}

    \newpage
    \section{СТОЛБЧАТАЯ МОДЕЛЬ ГЛОБАЛЬНОЙ ЭЛЕКТРИЧЕСКОЙ ЦЕПИ}
    \input{inc/1-1-theory}
    \input{inc/1-2-pract}
    \input{inc/1-3-results}
    % вывод уравнений на потенциал
    % реализация столбцовой модели ГЭЦ ? (тут про проводимости тинсли)
    % описание модели ГЭЦ с более простой проводимостью ??
    % сравнение двух моделей и оценка нужности учёта более тонкой параметризации проводимости
    \newpage
    \section{ВЛИЯНИЕ КОЛЕБАНИЯ МАДДЕНА--ДЖУЛИАНА НА ГЛОБАЛЬНУЮ ЭЛЕКТРИЧЕСКУЮ ЦЕПЬ}
    \input{inc/2-1-mjo-index}
    \input{inc/2-2-gec-simulation}
    \input{inc/2-3-vostok}
    \input{inc/2-4-mjo-model-gec}
    \input{inc/2-5-mjo-pg}
    \input{inc/2-6-further-analysis}
    \input{inc/2-7-futher-discussion}
    
    % ?? описание используемой модели ГЭЦ %
    % описание измерений ГП на станции Восток %
    % эффекты КМД в ГЭЦ, обнаруженные при моделировании
    % Большой и подробный раздел про объяснение вариации ИП по фазам КМД
    % Эффекты КМД в измерениях ГП
    % обсуждение причин несостыковок
    
    \newpage
    \input{inc/3-conclusion}
    % ЗАКЛЮЧЕНИЕ

    \newpage
    \addcontentsline{toc}{section}{СПИСОК ЛИТЕРАТУРЫ}
    \bibliographystyle{unsrt}
    %\bibliography{inc/references}
    \begin{thebibliography}{10}

\bibitem{Williams_Mareev_2014}
E.~Williams and E.~Mareev.
\newblock Recent progress on the global electrical circuit.
\newblock {\em Atmos.\ Res.}, 135--136:208--227, 2014.

\bibitem{Rycroft_et_al_2008}
M.~J. Rycroft, R.~G. Harrison, K.~A. Nicoll, and E.~A. Mareev.
\newblock An overview of {E}arth’s global electric circuit and atmospheric
  conductivity.
\newblock {\em Space Sci.\ Rev.}, 137(1--4):83--105, 2008.

\bibitem{Williams_2009}
E.~R. Williams.
\newblock The global electrical circuit: A review.
\newblock {\em Atmos.\ Res.}, 91(2--4):140--152, 2009.

\bibitem{Markson_2007}
R.~Markson.
\newblock The global circuit intensity: Its measurement and variation over the
  last 50 years.
\newblock {\em Bull.\ Amer.\ Meteor.\ Soc.}, 88(2):223--241, 2007.

\bibitem{Ilin_et_al_2020}
N.~V. Ilin, N.~N. Slyunyaev, and E.~A. Mareev.
\newblock Toward a realistic representation of global electric circuit
  generators in models of atmospheric dynamics.
\newblock {\em J.\ Geophys.\ Res.\ Atmos.}, 125(6):e2019JD032130, 2020.

\bibitem{Slyunyaev_et_al_2015}
N.~N. Slyunyaev, E.~A. Mareev, and A.~A. Zhidkov.
\newblock On the variation of the ionospheric potential due to large-scale
  radioactivity enhancement and solar activity.
\newblock {\em Journal of Geophysical Research: Space Physics},
  120(8):7060--7082, 2015.

\bibitem{Madden_Julian_1994}
R.~A. Madden and P.~R. Julian.
\newblock Observations of the 40–50-day tropical oscillation—{A} review.
\newblock {\em Mon.\ Wea.\ Rev.}, 122(5):814--837, 1994.

\bibitem{Zhang_2005}
C.~Zhang.
\newblock {M}adden-{J}ulian {O}scillation.
\newblock {\em Rev.\ Geophys.}, 43(2):RG2003, 2005.

\bibitem{Zhang_et_al_2020}
C.~Zhang, {\'A}.~F. Adames, B.~Khouider, B.~Wang, and D.~Yang.
\newblock Four theories of the {M}adden-{J}ulian {O}scillation.
\newblock {\em Rev.\ Geophys.}, 58(3):e2019RG000685, 2020.

\bibitem{Anyamba_et_al_2000}
E.~Anyamba, E.~Williams, J.~Susskind, A.~Fraser-Smith, and M.~Fullekrug.
\newblock The manifestation of the {M}adden–{J}ulian oscillation in global
  deep convection and in the {S}chumann resonance intensity.
\newblock {\em J.\ Atmos.\ Sci.}, 57(8):1029--1044, 2000.

\bibitem{Beggan_Musur_2019}
C.~D. Beggan and M.~A. Musur.
\newblock Is the {M}adden–{J}ulian {O}scillation reliably detectable in
  {S}chumann {R}esonances?
\newblock {\em J.\ Atmos.\ Sol.\ Terr.\ Phys.}, 190:108--116, 2019.

\bibitem{Slyunyaev_et_al_2021a}
N.~N. Slyunyaev, A.~V. Frank-Kamenetsky, N.~V. Ilin, F.~G. Sarafanov, M.~V.
  Shatalina, E.~A. Mareev, and C.~G. Price.
\newblock Electric field measurements in the {A}ntarctic reveal patterns
  related to the {E}l {N}iño—{S}outhern {O}scillation.
\newblock {\em Geophys.\ Res.\ Lett.}, 48(21):e2021GL095389, 2021.

\bibitem{Slyunyaev_et_al_2021b}
N.~N. Slyunyaev, N.~V. Ilin, E.~A. Mareev, and C.~G. Price.
\newblock The global electric circuit land–ocean response to the {E}l
  {N}iño—{S}outhern {O}scillation.
\newblock {\em Atmos.\ Res.}, 260:105626, 2021.

\bibitem{Harrison_et_al_2011}
R.~G. Harrison, M.~Joshi, and K.~Pascoe.
\newblock Inferring convective responses to {E}l {N}iño with atmospheric
  electricity measurements at {S}hetland.
\newblock {\em Environ.\ Res.\ Lett.}, 6(4):044028, 2011.

\bibitem{Slyunyaev_et_al_2021c}
N.~N. Slyunyaev, N.~V. Ilin, E.~A. Mareev, and C.~G. Price.
\newblock A new link between {E}l {N}iño—{S}outhern {O}scillation and
  atmospheric electricity.
\newblock {\em Environ.\ Res.\ Lett.}, 16(4):044025, 2021.

\bibitem{Mareev_2010}
Е.~А. Мареев.
\newblock Достижения и перспективы
  исследований глобальной электрической
  цепи.
\newblock {\em Усп. физ. наук}, 180(5):527--534, 2010.

\bibitem{Kalinin_et_al_2014}
А.~В. Калинин, Н.~Н. Слюняев, Е.~А. Мареев и
  А.~А. Жидков.
\newblock Стационарные и нестационарные модели
  глобальной электрической цепи:
  корректность, аналитические соотношения,
  численная реализация.
\newblock {\em Известия Российской Академии Наук.
  Физика Атмосферы и Океана}, 50(3):355--364, 2014.

\bibitem{Mareev_Volodin_2014}
E.~A. Mareev and E.~M. Volodin.
\newblock Variation of the global electric circuit and ionospheric potential in
  a general circulation model.
\newblock {\em Geophys.\ Res.\ Lett.}, 41(24):9009--9016, 2014.

\bibitem{Harrison_2012}
R.~Harrison.
\newblock The {C}arnegie curve.
\newblock {\em Surveys in Geophysics}, 34:209--232, 03 2012.

\bibitem{Madden_Julian_1972}
R.~A. Madden and P.~R. Julian.
\newblock Description of global-scale circulation cells in the tropics with a
  40–50 day period.
\newblock {\em J.\ Atmos.\ Sci.}, 29(6):1109--1123, 1972.

\bibitem{Wheeler_Hendon_2004}
M.~C. Wheeler and H.~H. Hendon.
\newblock An all-season real-time multivariate {MJO} index: Development of an
  index for monitoring and prediction.
\newblock {\em Mon.\ Wea.\ Rev.}, 132(8):1917--1932, 2004.

\bibitem{Wang_et_al_2018}
Feiyang Wang, Wenshou Tian, Fei Xie, Jiankai Zhang, and Yuanyuan Han.
\newblock Effect of {M}adden–{J}ulian oscillation occurrence frequency on the
  interannual variability of northern hemisphere stratospheric wave activity in
  winter.
\newblock {\em Journal of Climate}, 31:5031--5049, 2018.

\bibitem{Burns_et_al_2012}
G.~B. Burns, B.~A. Tinsley, A.~V. Frank‐Kamenetsky, O.~A. Troshichev,
  W.~J.~R. French, and A.~R. Klekociuk.
\newblock Monthly diurnal global atmospheric circuit estimates derived from
  {V}ostok electric field measurements adjusted for local meteorological and
  solar wind influences.
\newblock {\em J.\ Atmos.\ Sci.}, 69(6):2061--2082, 2012.

\bibitem{Burns_et_al_2017}
G.~B. Burns, A.~V. Frank-Kamenetsky, B.~A. Tinsley, W.~J. French, P.~Grigioni,
  G.~Camporeale, and E.~A. Bering.
\newblock Atmospheric global circuit variations from {V}ostok and {C}oncordia
  electric field measurements.
\newblock {\em J.\ Atmos.\ Sci.}, 74(3):783--800, 2017.

\bibitem{Knutson_Weickmann_1987}
T.~R. Knutson and K.~M. Weickmann.
\newblock 30–60 day atmospheric oscillations: Composite life cycles of
  convection and circulation anomalies.
\newblock {\em Mon.\ Wea.\ Rev.}, 115(7):1407--1436, 1987.

\bibitem{Slingo_et_al_1999}
J.~M. Slingo, D.~P. Rowell, K.~R. Sperber, and F.~Nortley.
\newblock On the predictability of the interannual behaviour of the
  {M}adden–{J}ulian {O}scillation and its relationship with {E}l {N}iño.
\newblock {\em Quart.\ J.\ Roy.\ Meteor.\ Soc.}, 125(554):583--609, 1999.

\bibitem{Lo_Hendon_2000}
F.~Lo and H.~H. Hendon.
\newblock Empirical extended-range prediction of the {M}adden–{J}ulian
  oscillation.
\newblock {\em Mon.\ Wea.\ Rev.}, 128(7):2528--2543, 2000.

\bibitem{Matthews_2000}
A.~J. Matthews.
\newblock Propagation mechanisms for the {M}adden-{J}ulian {O}scillation.
\newblock {\em Quart.\ J.\ Roy.\ Meteor.\ Soc.}, 126(569):2637--2651, 2000.

\bibitem{Kessler_2001}
W.~S. Kessler.
\newblock {EOF} representations of the {M}adden–{J}ulian oscillation and its
  connection with {ENSO}.
\newblock {\em J.\ Climate}, 14(13):3055--3061, 2001.

\bibitem{Adlerman_Williams_1996}
E.~J. Adlerman and E.~R. Williams.
\newblock Seasonal variation of the global electrical circuit.
\newblock {\em J.\ Geophys.\ Res.}, 101(D23):29679--29688, 1996.

\bibitem{Zhang_Moore_2015}
Z.~Zhang and J.~C. Moore.
\newblock {\em Mathematical and Physical Fundamentals of Climate Change}.
\newblock Elsevier, Amsterdam, Netherlands, 2015.

\bibitem{Lavigne_et_al_2017}
T.~Lavigne, C.~Liu, W.~Deierling, and D.~Mach.
\newblock Relationship between the global electric circuit and electrified
  cloud parameters at diurnal, seasonal, and interannual timescales.
\newblock {\em J.\ Geophys.\ Res.\ Atmos.}, 122(16):8525--8542, 2017.

\end{thebibliography}

\end{document}